LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-01-25 src/ms.tex
add small part about changing sc_params

This can be generalised to a population of many binary systems with ease. Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary. As an example, we can take the same parameters as above for 3 different binaries but vary the primary as $m_1 = [5, 10, 15] \unit{M_{\odot}}$. Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$.

>>>>

This can be generalised to a population of many binary systems with ease. Instead of inputting single values for each parameter, one can input arrays of values where each entry corresponds to a different binary. As an example, we can take the same parameters as above for 3 different binaries but vary the primary as $m_1 = [5, 10, 15] \unit{M_{\odot}}$. Using \lw{} we find that the SNR for each of these cases is $\rho = [2.47, 4.49, 7.85]$. \referee{This also need not be limited to a 4-year LISA mission. With \lw{} we can additionally specify various parameters for the detector. For example, using \lw{} we can find that, for a 5-year TianQin mission with no confusion noise, the SNR for each of these cases is $\rho = [1.07, 1.95, 3.41]$.}
